TacticToe: Learning to Prove with Tactics

### 2018-02-19 tactictoe_jv.tex
more

Even when developing one theory, the context is continually changing:
modules are open and local identifiers are defined. Therefore, it is unlikely
that code extracted from proof scripts is interpretable in any other part of
\holfour without any post-processing.
To solve this issue, we recursively replace each local identifier by its
definition until we are able to write any expression with global identifiers
only. And we prefix each global identifiers by its module.
We call this process globalization. The result is a standalone \sml code
executable in any \holfour theories.  In the absence of side effects, it is
interpreted in the same way across theories.
Therefore, we can guarantee that the behavior of recorded stateless tactics
does not change. And because an update on a stateful tactic
generally increases its strength, our prediction algorithm based on past
examples is still reasonably effective in this case.

\subsection{Implementation}
We describe in more details the implementation of the recording algorithm which
consists of 4 phases: proof script extraction, proof script globalization,
tactic unit wrapping and creation of tactic-goal pairs.

@@

The first line of this script file opens modules (called structures in \sml). Each of
them contains a list of global identifiers which become directly accessible in
the rest of the script.
A local identifier \texttt{LIST\_INDUCT\_TAC} is declared next, which is a
tactic that performs induction on lists. Below that, the theorem
\texttt{MAP\_APPEND} is proven.
The global tactic \texttt{STRIP\_TAC} first removes universal quantifiers. Then,
the goal is split into a base case and a inductive case. Finally, both of
theses cases are solved by \texttt{ASM\_REWRITE\_TAC [MAP, APPEND]}, which
rewrites assumptions with the help of theorems previously declared in this
theory.

>>>>

Even when developing one theory, the context is continually changing:
modules are opened and local identifiers are defined. Therefore, it is unlikely
that code extracted from proof scripts is interpretable in any other part of
\holfour without any post-processing.
To solve this issue, we recursively replace each local identifier by its
definition until we are able to write any expression with global identifiers
only. Similarly, we prefix each global identifier by its module.
We call this process \emph{globalization}. The result is a standalone \sml code
executable in any \holfour theory.  In the absence of side effects, it is
interpreted in the same way across theories.
Therefore, we can guarantee that the behavior of recorded stateless tactics
does not change. And because an update on a stateful tactic
generally increases its strength, our prediction algorithm based on past
examples is still reasonably effective in this case.

\subsection{Implementation}
We describe in more detail our implementation of the recording algorithm. It
consists of 4 phases: proof script extraction, proof script globalization,
tactic unit wrapping, and creation of tactic-goal pairs.

@@

The first line of this script file opens modules (called structures in \sml). Each of
the modules contains a list of global identifiers which become directly accessible in
the rest of the script.
A local identifier \texttt{LIST\_INDUCT\_TAC} is declared next, which is a
tactic that performs induction on lists. Below that, the theorem
\texttt{MAP\_APPEND} is proven.
The global tactic \texttt{STRIP\_TAC} first removes universal quantifiers. Then,
the goal is split into a base case and an inductive case. Finally, both
of these cases are solved by \texttt{ASM\_REWRITE\_TAC [MAP, APPEND]}, which
rewrites assumptions with the help of theorems previously declared in this
theory.
